---
title: "Reproducible console workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproducible console workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(LightLogWeb)
```

LightLogWeb uses the same plain functions in R and in Shiny. An `llw_dataset` retains an immutable raw stage and a separately prepared stage.

```{r}
dataset <- llw_dataset(
  LightLogR::sample.data.environment,
  metadata = list(
    variable = "MEDI",
    variable_name = "Melanopic EDI",
    variable_unit = "lx",
    timezone = "Europe/Berlin",
    coordinates = c(48.52, 9.06)
  ),
  name = "sample.data.environment"
)
quality <- llw_quality(dataset)
quality$value$overview
```

Preparation never overwrites `dataset$raw_data` and never imputes light values. Gaps can become explicit `NA` observations, implausible values can be invalidated with a reason, and participant-days can be filtered by a declared coverage rule.

```{r}
prepared <- llw_prepare(
  dataset,
  gap_policy = "explicit_na",
  value_range = c(0, 200000),
  interval = "5 min",
  daily_missing_max = 0.2
)
grouped <- llw_group(prepared, dimensions = c("participant", "date"))
```

Metric wrappers call the authoritative LightLogR functions. The registry supplies requirements, defaults, units, cautions, and online documentation links.

```{r}
llw_metric_registry()[, c("id", "requirement", "units", "documentation")]
metrics <- llw_metrics(
  grouped,
  list(
    list(id = "duration_above_threshold", parameters = list(threshold = 250)),
    list(id = "dose")
  )
)
metrics$value
```

A recipe makes the complete execution order portable.

```{r}
recipe <- llw_recipe() |>
  llw_recipe_add("preparation", list(gap_policy = "explicit_na", interval = "5 min")) |>
  llw_recipe_add("grouping", list(dimensions = c("participant", "date"))) |>
  llw_recipe_add("metric", list(metrics = list(list(id = "dose")))) |>
  llw_recipe_add("visualization", list(type = "timeline", id = "Participant"))

analysis <- llw_run(dataset, recipe)
script <- llw_build_script(recipe, data_expression = "LightLogR::sample.data.environment")
```

`llw_export()` writes CSV/RDS results and PNG/SVG/PDF figures. `llw_manifest()` records parameters, versions, citations, source fingerprints, and session information.
