---
title: "Authoring a custom analysis module"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Authoring a custom analysis module}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A custom module combines a namespaced Shiny screen with three plain functions: `validate()`, `run()`, and `code()`. `run()` must return `llw_result`; `code()` must return parseable R code. Startup modules are trusted R code. The interface controls state mutation and records reproducibility information, but it is not a process sandbox.

```{r}
library(LightLogWeb)

daily_mean_module <- llw_module(
  id = "daily_mean",
  title = "Daily mean exposure",
  version = "1.0.0",
  required_columns = c("Id", "Datetime", "MEDI"),
  docs_url = "https://example.org/daily-mean",

  ui = function(id) {
    ns <- shiny::NS(id)
    shiny::tagList(
      shiny::numericInput(ns("offset"), "Offset", 0),
      shiny::actionButton(ns("commit"), "Add to recipe")
    )
  },

  server = function(id, context) {
    shiny::moduleServer(id, function(input, output, session) {
      shiny::observeEvent(input$commit, {
        context$commit(list(offset = input$offset), label = "Daily mean exposure")
      })
    })
  },

  validate = function(data, metadata, params) {
    stopifnot(is.numeric(params$offset), length(params$offset) == 1)
    TRUE
  },

  run = function(data, metadata, params) {
    table <- data |>
      dplyr::mutate(Date = as.Date(.data$Datetime, tz = metadata$timezone)) |>
      dplyr::group_by(.data$Id, .data$Date) |>
      dplyr::summarise(mean_exposure = mean(.data[[metadata$variable]], na.rm = TRUE) + params$offset, .groups = "drop")
    llw_result(
      "table", table,
      label = "Daily mean exposure",
      units = metadata$variable_unit,
      parameters = params,
      grouping = c("Id", "Date"),
      source = "daily_mean",
      data = table
    )
  },

  code = function(params) {
    paste0(
      "data |> dplyr::mutate(Date = as.Date(Datetime)) |>",
      " dplyr::group_by(Id, Date) |>",
      " dplyr::summarise(mean_exposure = mean(MEDI, na.rm = TRUE) + ",
      params$offset, ", .groups = 'drop')"
    )
  }
)
```

The module is fully testable without Shiny.

```{r}
dataset <- llw_dataset(LightLogR::sample.data.environment)
result <- llw_run_module(dataset, daily_mean_module, list(offset = 0))
head(result$value)
```

Pass modules at startup in the order they should appear after Visualize.

```{r, eval=FALSE}
LightLogWeb(modules = list(daily_mean_module))
```

The server receives read-only reactives at `context$raw`, `prepared`, `grouped`, `metadata`, `recipe`, and `selection`. It may request a controlled recipe change with `context$commit(params)` and publish an `llw_result` with `context$publish(result)`. It must not mutate core objects directly.

Duplicate IDs fail at startup. Missing required columns fail before calculation. A project with a missing or version-incompatible module retains the stored step in a disabled state with an actionable warning.
